\documentclass{article}
\usepackage[utf8]{inputenc}
\title{North South University\\Game Archive System\\CSE311 Lab Project}
\author{Group Members:\\1.Name:- Md. Sajjad Hossain\\ID:- 1922000042\\Section:-5}
\date{July 24, 2021}

\begin{document}

\maketitle

\section{Introduction:} By game archive system we meant a collection or hub of numerous games arranged in a order by genre so that a player or a manager of the game developing company can easily take a look at the features/upgrades, story preview and so on. There are actually two sides of this system one is server side and the other is client side. Server side is actually the company's side in which a person of the company with the authorisation can make changes and add or alter information of games. The client side is an interface in which a person can make purchases and download a game he wants. Then the total downloads or purchases of a game is stored and managed thoroughly inside the server and proper marketing is done according to players review, total downloads, price range and so on. New games should be published before the release and pre-register facility will be provided through special interface.

\section{Objective:}
1. A gamer can easily make purchase or download a game online through online payment system like bitcoin, visa/mastercard, bkash/rocket/nogod(Only valid in Bangladesh).
2. A player can experience many options thoroughly integrated with the game company, sometimes discount is provided for a number purchase limit to particular customers.
3. Notification/messages for system requirement if a game is not compatible with the device. And of course there will be a explicit statement about the game a player can see before making a purchase.
4. Notification will be given to users for update features of games.
5. Some licensed/restricted games for some users will be purchased or renewed after particular period of time. There will be different purchase options here also monthly,3 month, yearly.
6. Users will be notified about license expiry if licensed purchase is made.
7. All features of a game will be described and games will arranged by type. So that a player can easily go through the area of interest he wants to, all in a collection.

\section{Target Customers:}
1. Video game players-People who are interested in playing games and purchasing games.
2. Game developers-There will be a particular section interface in which job offers are given and qualified candidates are hired according to their skill set through competitive assessment.

\section{Value Proposition:}
This system will manage online selling and buying process of games with relational data base management system and interface. There are different game companies like EA, Ubisoft, nvidia, tencent who are of this type of company. We are here to enhance the user virtual experience level through a whole new dimension. The hassles of third party purchase will be disappeared and different countries purchase options will be handled an d manipulated by management teams. Any organisation selling our products without copyright permission will be handled properly through law of information  technology act.

\section{Web Application Feature and description:}
Web page could be viewed by anyone, new users have to sign up old
users should be able to sign in. Every information of a particular user will be saved in the database starting from personal information to purchase information and other. through an easy user-friendly process a person should be able tom download or purchase games. A payment process would be added and verified by our team before an actual purchase is made. Once account creation process is completed the below points to be added:-
1. Buy or download games.
2. Can preview the gameplay just before the purchase.
3. A trial version of games can be purchased for free for certain duration, after that services will be off.
4. Give review and rate.
5. Past purchase information will be available.
6. Upgrades and features addition to a game will be managed and notified.
As there will be two user end of the web site. The hiring information will be managed separately. The following feature would be added to hiring page, want for:
1. Academic and programming certifications and achievements.
2. Past work experiences.
3. Virtual environment making experience and skills.
4. Previous related projects they worked for.
5. A set of contests for being selected for the job.
\section{Tools and Resources:}
HTML
Javascript,
MySQL,
PHP,
Web server,
API for sms.
\section{Challenge:}
A lot of work is to be done for each section of the project as it is a broad project. Separate and huge information would be stored and managed for client and server end. The maintenance would be complex and huge costly. Data given about payment and purchase is to be verified and managed which is complex. User interface for users should be made easy to use. 

\end{document}
